Paper Four Summary

### 2015-09-24 hw/read/4/summary.tex
added motivational statement

\section*{Feature Extraction}
\begin{description}
\item [{Motivational~statements}]
\end{description}

>>>>

\section*{Feature Extraction}
\begin{description}
\item [{Motivational~statements}] The motivation of this paper is to apply AntMiner+, a rule-based Ant Colony Optimization classification technique to public repositories and assess it's prediction and inference capabilities against other previously successful classification techniques in the domain of software quality.
\end{description}
